\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{enumerate}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}

% No page numbers
%\pagenumbering{gobble}

% INFORMATION SHEET ---------------------------------------------
\newcommand{\addinformationsheet}{
\clearpage
\thispagestyle{empty}
\begin{center}
\LARGE{\bf \textsf{Information sheet\\CS224W: Social and Information Network Analysis}} \\*[4ex]
\end{center}
\vfill
\textbf{Assignment Submission } Fill in and include this information sheet with each of your assignments.  This page should be the last page of your submission.  Assignments are due at 11:59pm and are always due on a Thursday.  All students (SCPD and non-SCPD) must submit their homeworks via GradeScope (\url{http://www.gradescope.com}). Students can typeset or scan their homeworks. Make sure that you answer each (sub-)question on a separate page. That is, one answer per page regardless of the answer length. Students also need to upload their code at \url{http://snap.stanford.edu/submit}. Put all the code for a single question into a single file and upload it. Please do not put any code in your GradeScope submissions. 
\\
\\
\textbf{Late Homework Policy } Each student will have a total of {\em two} free late periods. {\em Homeworks are due on Thursdays at 11:59pm PDT and one late period expires on the following Monday at 11:59pm PDT}.  Only one late period may be used for an assignment.  Any homework received after 11:59pm PDT on the Monday following the homework due date will receive no credit.  Once these late periods are exhausted, any assignments turned in late will receive no credit.
\\
\\
\textbf{Honor Code } We strongly encourage students to form study groups. Students may discuss and work on homework problems in groups. However, each student must write down their solutions independently i.e., each student must understand the solution well enough in order to reconstruct it by him/herself.  Students should clearly mention the names of all the other students who were part of their discussion group. Using code or solutions obtained from the web (github/google/previous year solutions etc.) is considered an honor code violation. We check all the submissions for plagiarism. We take the honor code very seriously and expect students to do the same. 
\vfill
\vfill
}
% ------------------------------------------------------------------------------

% MARGINS (DO NOT EDIT) ---------------------------------------------
\oddsidemargin  0in \evensidemargin 0in \topmargin -0.5in
\headheight 0.25in \headsep 0.25in
\textwidth   6.5in \textheight 9in
\parskip 1.5ex  \parindent 0ex \footskip 20pt
% ---------------------------------------------------------------------------------

% HEADER (DO NOT EDIT) -----------------------------------------------
\newcommand{\problemnumber}{0}
\newcommand{\myname}{name}
\newfont{\myfont}{cmssbx10 scaled 1200}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[L]{\myfont Question \problemnumber, Problem Set 0, CS224W}
%\fancyhead[R]{\bssnine \myname}
\newcommand{\newquestion}[1]{
\clearpage % page break and flush floats
\renewcommand{\problemnumber}{#1} % set problem number for header
\phantom{}  % Put something on the page so it shows
}
% ---------------------------------------------------------------------------------




% BEGIN HOMEWORK HERE
\begin{document}

% Question 1.1
\newquestion{1.1}
7115
% Question 1.2
\newquestion{1.2}
0
% Question 1.3
\newquestion{1.3}
103689
% Question 1.4
\newquestion{1.4}
100762
% Question 1.5
\newquestion{1.5}
2927
% Question 1.6
\newquestion{1.6}
1005
% Question 1.7
\newquestion{1.7}
4734
% Question 1.8
\newquestion{1.8}
1612
% Question 1.9
\newquestion{1.9}
5165
% Question 2.1
\newquestion{2.1}
24
% Question 2.2
\newquestion{2.2}
Number of Nodes: 7066

Number of Edges: 103663
% Question 2.3
\newquestion{2.3}
4037
15
6634
% Question 2.4
\newquestion{2.4}
Top 3 Hubs: 2565, 766,2688

Top 3 Authorities: 2398, 4037, 3352
% Information sheet
% Fill out the information below (this should be the last page of your assignment)
\addinformationsheet
{\Large
\textbf{Your name: } Bowen Yao  % Put your name here
\\
\textbf{Email:} boweny@stanford.edu{\hspace*{7cm}}  % Put your e-mail here
\textbf{SUID:} \hrulefill  06129749% Put your student ID here
\\*[2ex] 
}
Discussion Group:   None% List your study group here
\\
\vfill\vfill
I acknowledge and accept the Honor Code.\\*[3ex]
\bigskip
\textit{(Signed)} 
BY% Replace this line with your initials
\vfill





\end{document}
